Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

        We find that the stream is successfully recovered in both astrometric and
        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ stream
        stars being recovered with membership probability greater than $80\%$.
        In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
        synthetic data color-coded by stream membership probability (top) and
        background membership probability (background) for different $\phi_1$
        slices. Importantly, the photometric portion of the mixture model
        successfully identifies the stream in magnitude space, showing a high stream
        membership probability where the stream is present, and a low probability
        ($\sim 0$) where the stream is absent.
        The false positive rate (i.e., stars misidentified as stream members) for this test
        is found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
        the 80\% membership probability threshold.
        % The perfect recovery rate and low false identification rate demonstrate the efficacy
        % of this method.

@@

        \begin{enumerate}
            \item Gaia data.
                \begin{enumerate}
                    \item box size
                    \item selection criteria
                \end{enumerate}
            \item crossmatched with panstarrs1
            \item extinction corrected with bayestar2019
        \end{enumerate}

>>>>

        We find that the stream is successfully recovered in both astrometric and
        photometric coordinates, with $\variable{output/mock/ncorrect_variable.txt}\%$ of stream
        stars being recovered with membership probability greater than $80\%$.
        In the bottom two rows of \autoref{fig:mock_data_result} we illustrate the
        synthetic data color-coded by stream membership probability (top) and
        background membership probability (background) for different $\phi_1$
        slices. Importantly, the photometric portion of the mixture model
        successfully identifies the stream in magnitude space, showing a high stream
        membership probability where the stream is present, and a low probability
        ($\sim 0$) where the stream is absent.
        The false positive rate (i.e., stars misidentified as stream members) for this test
        is found to be $\variable{output/mock/falseident_variable.txt}\%$ when cutting on
        the 80\% membership probability threshold.
        % The perfect recovery rate and low false identification rate demonstrate the efficacy
        % of this method.

@@

        % \begin{enumerate}
        %     \item Gaia data.
        %         \begin{enumerate}
        %             \item box size
        %             \item selection criteria
        %         \end{enumerate}
        %     \item crossmatched with panstarrs1
        %     \item extinction corrected with bayestar2019
        % \end{enumerate}
